Batched Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design

### 2018-02-03 paper/abstract.tex
Paper update

\begin{abstract} 
    The Bayesian optimization has recently shown promising performance for
    automated analog circuit design. However, the sequential property of
    Bayesian optimization limits its further application. In this paper, a
    batched bayesian optimization method is proposed, the parallelization is
    realized via a multi-objective ensemble of acquisition functions. In each
    iteration, multiple acquisition functions are selected, the multi-objective
    optimization is then performed to search for the Pareto front of the
    acquisition functions, candidate points are then sampled from the Pareto
    front. The proposed method is compared with several state-of-the-art
    batched Bayesian optimization algorithms using analytical benchmark
    functions and real-world analog circuits; the experimental results show
    that the proposed method is competitive compared to the state-of-the-art
    methods.
\end{abstract}

>>>>

\begin{abstract} 
    The Bayesian optimization algorithm has recently shown promising
    performance for the automated design analog integrated circuits. However,
    the sequential property of Bayesian optimization limits its further
    application. In this paper, a batched bayesian optimization algorithm is
    proposed, the parallelization is realized via a multi-objective ensemble of
    acquisition functions. In each iteration, multiple acquisition functions
    are selected, the multi-objective optimization is performed to search for
    the Pareto front of the acquisition functions, candidate points are then
    sampled from the Pareto front. The proposed method is compared with several
    state-of-the-art batched Bayesian optimization algorithms using analytical
    benchmark functions and real-world analog circuits; the experimental
    results show that the proposed method is competitive compared to the
    state-of-the-art algorithms.
\end{abstract}

### 2018-02-03 paper/intro.tex
Paper update

% % TODO: more introduction to the importance of anlog IC sizing, as the reviewers may not have much knowledge of circuit design
Automated analog circuit design has been a challenging problem for the
community of electronic design automation (EDA). Unlike digital circuits, where
the design flow is highly automated, analog circuit design still
heavily relies on designer's experience. The design parameters of analog circuits like
transistor widths and lengths need to be manually calculated based on the
specifications and the designers' understanding of the circuit. However, due to
the ever-scaling IC manufacture technology and the increasing demands for
high-performance, low-power circuits, it is getting much more difficult to meet
the performance and time-to-market requirement with manual circuit design.
Automated analog circuit design has thus attracted more research interests in
the past decade~\cite{rutenbar2007hierarchical}.

% TODO: Traditional methods using offline model and simulated based methods are
% not good
The analog circuit design automation problems can be formulated as optimization
problems, the aim is to find the optimal vector of design parameters that give
the best figure of merit (FOM). Prior works about analog circuit optimization
include offline model-based approaches
~\cite{colleran2003optimization,daems2003simulation,wang2014enabling} and
simulation-based approaches. The offline model-based methods try to build
accurate global models and then apply global optimization algorithms to the
cheap-to-evaluate models. The model either comes from designers' manual
derivation or regression models like SVM and ANN. The problem of this approach
is that the accurate models are usually hard to get, for example,
in~\cite{wang2014enabling}, 100,000 randomly simulated points are used to train
a sparse polynomial model for a circuit with ten design parameters.
Simulation-based methods, instead, treat the circuits as black-box functions
that get the FOM value from circuit simulations, global optimization algorithms
are then directly applied to the black-box functions. For simulation-based
circuit optimization methods, meta-heuristic
algorithms~\cite{phelps2000anaconda, liu2009analog} are widely used, although
these algorithms can explore the whole design space, they have relatively low
convergence rate and consume many circuit simulations. When the circuit
simulation takes a long time, both model-based and simulation-based approaches
can be very time-consuming.

>>>>

% % TODO: more introduction to the importance of anlog IC sizing, as the reviewers may not have much knowledge of circuit design
%
The advancement of modern society is driven by the development of integrated
circuits (IC), unlike the digital circuits where the design flow is already
highly automated, the automation of analog circuit design is still a
challenging problem.

For analog circuits, the design parameters like widths and lengths of
transistors are manually calculated by designers with their experience and the
understanding of the design specifications. However, due to the progress of IC
manufacture technology forecasted by Moore's law, the circuit devices become
more and more complicated, and the parasitic effect of the circuit can no
longer be ignored; on the other hand, the demands for high-performance,
low-power analog circuits is increasing. It is getting much more difficult to
meet the performance and time-to-market requirement with manual designing.
Automated analog circuit design has thus attracted more research interests in
the past decade~\cite{rutenbar2007hierarchical}.

% TODO: Traditional methods using offline model and simulated based methods are
% not good
The analog circuit design automation problems can be formulated as optimization
problems, the aim is to find the optimal vector of design parameters that give
the best figure of merit (FOM). Prior works about analog circuit optimization
include offline model-based approaches
~\cite{colleran2003optimization,daems2003simulation,wang2014enabling} and
simulation-based approaches. The offline model-based methods try to build
accurate global models and then optimize the cheap-to-evaluate models. The
model either comes from designers' manual derivation or regression models like
SVM and ANN. The problem of this approach is that the accurate models are
usually hard to get; for example, in~\cite{wang2014enabling}, 100,000 randomly
simulated points are used to train a sparse polynomial model for an amplifier
circuit with ten design parameters. Simulation-based methods, instead, treat
the circuits as black-box functions that get the FOM values from circuit
simulations, global optimization algorithms are then directly applied to the
black-box functions.  For simulation-based circuit optimization methods,
meta-heuristic algorithms~\cite{phelps2000anaconda, liu2009analog} are widely
used, although these algorithms can explore the whole design space, they have
relatively low convergence rate. When the circuit simulation takes a long time,
both model-based and simulation-based approaches can be very time-consuming.
